---
title: "Explore_script_fulldata"
output: html_document
date: "2024-02-16"
---

## Load packages and data

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(haven)
library(psych)
library(mice)
```

## Data wrangling

### Data selection

```{r}
rm(nomem_encr, liss4, liss7, result_df, lisswhat)
```

load all variables

```{r}
df_whatapp <- read.csv("C:/Users/danch/OneDrive/2 Course MS/Thesis/Data/df_what.csv", header=TRUE)
df_liss <- read.csv("C:/Users/danch/OneDrive/2 Course MS/Thesis/Data/df_liss.csv", header=TRUE)
# Background
lissback <- read_sav("C:/Users/danch/OneDrive/2 Course MS/Thesis/Data/lissback/avars_202309_EN_1.0p.sav")
```

### Data merging

detach control variables

```{r}
df_whatapp <- df_whatapp[,-c(132:159)]
```

join dataframes, attach liss panels to a whats app study

```{r}
df_res <- df_whatapp %>% 
  left_join(df_liss, by = "nomem_encr")
```

attach control variables

```{r}
df_res <- df_res %>% 
  left_join(lissback, by = "nomem_encr")
```

### Processing

save dataframe with non_respondents == 1 excluded

```{r}
#dfnor <- df[df$non_respondents != 1,]
```

Introduce alternative messenger variable

```{r}
df_res$alt_chat_use <- ifelse(df_res$QA10b != 7 | df_res$QA10c != 7, 1, 0) # 1 if alt messenger is used at least almost never, 0 otherwise
```

Split alt_chat_use into other_messenger and secure_messenger.

```{r}
df_res$secure_messenger <- df_res$alt_chat_use
#df$alt_chat_use <- NULL
df_res$other_messenger <- ifelse(nchar(as.character(df_res$QA10f_text)) > 0, 1, 0)
```

#### Fixing scales

```{r}
# if df_res$cp23o019 ==-9, then NA
df_res$cp23o019[df_res$cp23o019 == -9] <- NA

# if  df_res$nettocat == 13 or 14, then NA

df_res$

df_res$nettocat[df_res$nettocat == 13] <- NA
df_res$nettocat[df_res$nettocat == 14] <- NA

# if geslacht = 3, then NA

df_res$geslacht[df_res$geslacht == 3] <- NA
```

#### Recoding

If NA for Q11, then recode as 0

```{r}
df_res$QA11 <- ifelse(is.na(df_res$QA11), 0, df_res$QA11)
```

Recode age to include it

```{r}
df_res$gebjaar_nm <- 2023 - df_res$gebjaar 
```

Education recode

```{r}
df_res$oplcat_bin <- ifelse(df_res$oplcat %in% c(1, 2, 3), 0, 1)
```

Add Employment variable

```{r}
df_res$belbezig <- ifelse(df_res$belbezig %in% c(1, 2, 3), 1, 0)
```

#### Correctness Check

Are everything encoded as needed?

##### DV's

```{r}
df_res$df_res <- NULL

table(df_res$donators)
table(df_res$status)

# recode status so that  1 is assigned to non-respondents, 2 is assigned to non-compliers, 3 is assigned to non-contributors, and 4 is assigned to donators, Screened out are marked as NA
```

##### Predictors

```{r}
table(df_res$QA5)
table(df_res$QA10a)
table(df_res$QA7)
table(df_res$alt_chat_use)
table(df_res$altruism)
table(df_res$cp23o136)
table(df_res$cs22o283)
table(df_res$cp23o019)
table(df_res$geslacht)
table(df_res$gebjaar_nm)
table(df_res$nettocat)
table(df_res$oplcat_bin)
table(df_res$belbezig)
```

select only data needed in analysis

```{r}
df_res_trim <- df_res %>% 
  select(nomem_encr, donators, status, QA5, QA10a, QA7, alt_chat_use, altruism, cp23o136, cs22o283, cp23o019, geslacht, gebjaar_nm, nettocat, oplcat_bin, belbezig, agreab, extrov, conscient, neurot, openess)
```

#### Missing Data Handling

-   Identify and visualize missing data patterns.

```{r}
#md.pattern(df_res_trim)

## calculate number of missing values
(2232*100)/4800

## calculate number of distinct patterns of missing data
n_distinct_missing <- nrow(md.pattern(df_res_trim))
n_distinct_missing
```
Now, for the missing data, we will use the mice package to impute the missing data.

```{r}
#str(df_res_trim)
# recode as ordinal, geslacht and nettocat 
df_res_trim$geslacht <- as.ordered(df_res_trim$geslacht)
df_res_trim$nettocat <- as.ordered(df_res_trim$nettocat)
```

```{r}
imputed_data <- mice(df_res_trim, m = 5, method = 'pmm', seed = 500)
imputed_data$imp
df_res_trim <- complete(imputed_data)
rm(imputed_data)
```

Attach step to data without missingness

```{r}
df_res <- df_res %>%
  mutate(step = case_when(
    non_respondents == 1 ~ 1,
    non_compliers == 1 ~ 2,
    non_donators == 1 ~ 3,
    donators == 1 ~ 4,
    screened_out == 1 ~ NA_real_,
    TRUE ~ as.numeric(status)  # Assuming 'status' is numeric; if it's a factor or character, use as.numeric(as.character(status))
  ))

# if status == screened_out, then step == NA

df_res$step[df_res$status == "screened_out"] <- NA
df_res_trim$step <- df_res$step

# if step == NA, then use is.na to make donators NA

df_res_trim$donators[is.na(df_res_trim$step)] <- NA
```

also, attach AccountPackageID

```{r}
# use nomem_encr to attach AccountPackageID from df_res to df_res_trim

df_res_trim <- left_join(df_res_trim, df_res %>% select(nomem_encr, AccountPackageID), by = "nomem_encr")
```

## Exploratory Analysis

### Descriptive Analysis

-   Calculate summary statistics like mean, median, and standard deviation.

```{r}
describe(df_res_trim)
```

## Univariate Analysis for controls

```{r}
hist_plot_all <- ggplot(df_res, aes(x = leeftijd, fill = factor(status))) +
  geom_histogram(binwidth = 0.5, alpha = 0.7) +
  labs(
    title = "Donation Status",
    x = "Age",
    y = "Frequency"
  )  +
  scale_fill_manual(values = c("donators" = "#FF5733", "non_compliers" = "#3498db",   "non_donators" = "#27ae60", "screened_out" = "#f1c40f", "non_respondents" = "#95a5a6"),
                    labels = c("donators" = "Donators", "non_compliers" = "Non-compliers",   "non_donators" = "Non-donators", "screened_out" = "Screened out", "non_respondents" = "Non-respondents")) +
  scale_x_continuous(breaks = seq(0, 100, by = 5)) +
  scale_y_continuous(breaks = seq(0, 100, by = 5)) +
  theme_minimal()
hist_plot_all
```

```{r}
dfper <- data.frame(df_res$leeftijd, as.factor(df_res$status))
table(dfper)
prop.table(table(dfper),1)
probs <- data.frame(prop.table(table(dfper),1))
probs$Freq <- probs$Freq*100
colnames(probs) <- c("leeftijd", "status", "Freq")
colnames(probs)
probs
```

```{r}
hist_plot_all <- ggplot(probs, aes(x = leeftijd, y = Freq, fill = status)) +
  geom_bar(stat = "identity", position = "stack", alpha = 0.7) +
  labs(
    title = "Donation Status",
    x = "Age",
    y = "Percentage"
  )  +
  scale_fill_manual(values = c("donators" = "#FF5733", "non_compliers" = "#3498db", "non_donators" = "#27ae60", "screened_out" = "#f1c40f", "non_respondents" = "#95a5a6"),
                    labels = c("donators" = "Donators", "non_compliers" = "Non-compliers", "non_donators" = "Non-donators", "screened_out" = "Screened out", "non_respondents" = "Non-respondents"))  +
  scale_y_continuous(labels = scales::percent_format(scale = 1), expand = c(0, 0)) +
  theme_minimal()
hist_plot_all
```


```{r}
filtered_df <- df_res[df_res$sted > -1, ]

hist_plot_all <- ggplot(filtered_df, aes(x = sted, fill = factor(status))) +
  geom_histogram(binwidth = 0.5, alpha = 0.7) +
  labs(
    title = "Donation Status",
    x = "Urbanisation (1 - strongly urban)",
    y = "Frequency"
  )  +
  scale_fill_manual(values = c("donators" = "#FF5733", "non_compliers" = "#3498db",   "non_donators" = "#27ae60", "screened_out" = "#f1c40f", "non_respondents" = "#95a5a6"),
                    labels = c("donators" = "Donators", "non_compliers" = "Non-compliers",   "non_donators" = "Non-donators", "screened_out" = "Screened out", "non_respondents" = "Non-respondents")) +
  theme_minimal()
hist_plot_all
```

```{r}
filtered_df <- df_res[df_res$brutoink < 15000, ]

hist_plot_all <- ggplot(filtered_df, aes(x = brutoink, fill = factor(status))) +
  geom_density(alpha = 0.5) +
  labs(
    title = "Donation Status",
    x = "Income",
    y = "Frequency"
  )  +
  scale_fill_manual(values = c("donators" = "#FF5733", "non_compliers" = "#3498db",   "non_donators" = "#27ae60", "screened_out" = "#f1c40f", "non_respondents" = "#95a5a6"),
                    labels = c("donators" = "Donators", "non_compliers" = "Non-compliers",   "non_donators" = "Non-donators", "screened_out" = "Screened out", "non_respondents" = "Non-respondents")) +
  theme_minimal()
hist_plot_all
```

```{r}
hist_plot_all <- ggplot(df_res, aes(x = oplzon, fill = factor(status))) +
  geom_histogram(binwidth = 0.5, alpha = 0.7) +
  labs(
    title = "Donation Status",
    x = "Education (1 - primary, 6 - WED)",
    y = "Frequency"
  )  +
  scale_fill_manual(values = c("donators" = "#FF5733", "non_compliers" = "#3498db",   "non_donators" = "#27ae60", "screened_out" = "#f1c40f", "non_respondents" = "#95a5a6"),
                    labels = c("donators" = "Donators", "non_compliers" = "Non-compliers",   "non_donators" = "Non-donators", "screened_out" = "Screened out", "non_respondents" = "Non-respondents")) +
  theme_minimal()
hist_plot_all
```

```{r}
dfper <- data.frame(df_res$oplzon, as.factor(df_res$status))
table(dfper)
prop.table(table(dfper),1)
probs <- data.frame(prop.table(table(dfper),1))
probs$Freq <- probs$Freq*100
colnames(probs) <- c("oplzon", "status", "Freq")
colnames(probs)
probs
```

```{r}
hist_plot_all <- ggplot(probs, aes(x = oplzon, y = Freq, fill = status)) +
  geom_bar(stat = "identity", position = "stack", alpha = 0.7) +
  labs(
    title = "Donation Status",
    x = "Education (1 - primary, 6 - WED)",
    y = "Percentage"
  )  +
  scale_fill_manual(values = c("donators" = "#FF5733", "non_compliers" = "#3498db", "non_donators" = "#27ae60", "screened_out" = "#f1c40f", "non_respondents" = "#95a5a6"),
                    labels = c("donators" = "Donators", "non_compliers" = "Non-compliers", "non_donators" = "Non-donators", "screened_out" = "Screened out", "non_respondents" = "Non-respondents"))  +
  scale_y_continuous(labels = scales::percent_format(scale = 1), expand = c(0, 0)) +
  theme_minimal()
hist_plot_all
```

```{r}
hist_plot_all <- ggplot(df_res, aes(x = geslacht, fill = factor(status))) +
  geom_histogram(binwidth = 0.5, alpha = 0.7) +
  labs(
    title = "Donation Status",
    x = "Sex (1 - male, 2 - female 3 - other)",
    y = "Frequency"
  )  +
  scale_fill_manual(values = c("donators" = "#FF5733", "non_compliers" = "#3498db",   "non_donators" = "#27ae60", "screened_out" = "#f1c40f", "non_respondents" = "#95a5a6"),
                    labels = c("donators" = "Donators", "non_compliers" = "Non-compliers",   "non_donators" = "Non-donators", "screened_out" = "Screened out", "non_respondents" = "Non-respondents")) +
  theme_minimal()
hist_plot_all
```

## Univariate analysis for the independent variables

```{r}
hist_plot_all <- ggplot(df_res, aes(x = cp23o019, fill = factor(status))) +
  geom_histogram(binwidth = 0.5, alpha = 0.7) +
  labs(
    title = "Generalized Trust Question",
    x = "(1 - can't be too careful; 10 - Most people can be trusted)",
    y = "Frequency"
  )  +
  scale_fill_manual(values = c("donators" = "#FF5733", "non_compliers" = "#3498db",   "non_donators" = "#27ae60", "screened_out" = "#f1c40f", "non_respondents" = "#95a5a6"),
                    labels = c("donators" = "Donators", "non_compliers" = "Non-compliers",   "non_donators" = "Non-donators", "screened_out" = "Screened out", "non_respondents" = "Non-respondents")) +
  theme_minimal()
hist_plot_all
```

```{r}
filtered_df <- df_res
filtered_df$org_env_binary <- ifelse(filtered_df$org_env == "no connection", 0, 1)
filtered_df$org_hum_binary <- ifelse(filtered_df$org_hum == "no connection", 0, 1)

hist_plot_all <- ggplot(filtered_df, aes(x = org_hum_binary, fill = factor(status))) +
  geom_histogram(binwidth = 0.5, alpha = 0.7) +
  labs( title = "Altruism Question")  +
  scale_fill_manual(values = c("donators" = "#FF5733", "non_compliers" = "#3498db",   "non_donators" = "#27ae60", "screened_out" = "#f1c40f", "non_respondents" = "#95a5a6"),
                    labels = c("donators" = "Donators", "non_compliers" = "Non-compliers",   "non_donators" = "Non-donators", "screened_out" = "Screened out", "non_respondents" = "Non-respondents")) +
  theme_minimal()

hist_plot_all_2 <- ggplot(filtered_df, aes(x = org_env_binary, fill = factor(status))) +
  geom_histogram(binwidth = 0.5, alpha = 0.7) +
  labs( title = "Altruism Question")  +
  scale_fill_manual(values = c("donators" = "#FF5733", "non_compliers" = "#3498db",   "non_donators" = "#27ae60", "screened_out" = "#f1c40f", "non_respondents" = "#95a5a6"),
                    labels = c("donators" = "Donators", "non_compliers" = "Non-compliers",   "non_donators" = "Non-donators", "screened_out" = "Screened out", "non_respondents" = "Non-respondents")) +
  theme_minimal()

hist_plot_all
hist_plot_all_2
```

## Exploratory Analysis (Screened-out respondents excluded)

```{r}
df_res_nosc <- df_res[df_res$status != "screened_out",]
```

### Descriptive Analysis

```{r}
describe(df_res)
```

### Univariate Analysis for all

```{r}
hist_plot_all <- ggplot(df_res_nosc, aes(x = leeftijd, fill = factor(status))) +
  geom_histogram(binwidth = 0.5, alpha = 0.7) +
  labs(
    title = "Donation Status",
    x = "Age",
    y = "Frequency"
  )  +
  scale_fill_manual(values = c("donators" = "#FF5733", "non_compliers" = "#3498db",   "non_donators" = "#27ae60", "screened_out" = "#f1c40f", "non_respondents" = "#95a5a6"),
                    labels = c("donators" = "Donators", "non_compliers" = "Non-compliers",   "non_donators" = "Non-donators", "screened_out" = "Screened out", "non_respondents" = "Non-respondents")) +
  scale_x_continuous(breaks = seq(0, 100, by = 5)) +
  scale_y_continuous(breaks = seq(0, 100, by = 5)) +
  theme_minimal()
hist_plot_all
```


```{r}
dfper <- data.frame(df_res_nosc$leeftijd, as.factor(df_res_nosc$status))
#table(dfper)
#prop.table(table(dfper),1)
probs <- data.frame(prop.table(table(dfper),1))
probs$Freq <- probs$Freq*100
colnames(probs) <- c("leeftijd", "status", "Freq")
#colnames(probs)
#probs
```

```{r}
hist_plot_all <- ggplot(probs, aes(x = leeftijd, y = Freq, fill = status)) +
  geom_bar(stat = "identity", position = "stack", alpha = 0.7) +
  labs(
    title = "Donation Status",
    x = "Age",
    y = "Percentage"
  )  +
  scale_fill_manual(values = c("donators" = "#FF5733", "non_compliers" = "#3498db", "non_donators" = "#27ae60", "screened_out" = "#f1c40f", "non_respondents" = "#95a5a6"),
                    labels = c("donators" = "Donators", "non_compliers" = "Non-compliers", "non_donators" = "Non-donators", "screened_out" = "Screened out", "non_respondents" = "Non-respondents"))  +
  scale_y_continuous(labels = scales::percent_format(scale = 1), expand = c(0, 0)) +
  theme_minimal()
hist_plot_all
```


```{r}
hist_plot_all <- ggplot(df_res_nosc, aes(x = oplzon, fill = factor(status))) +
  geom_histogram(binwidth = 0.5, alpha = 0.7) +
  labs(
    title = "Donation Status",
    x = "Education (1 - primary, 6 - WED)",
    y = "Frequency"
  )  +
  scale_fill_manual(values = c("donators" = "#FF5733", "non_compliers" = "#3498db",   "non_donators" = "#27ae60", "screened_out" = "#f1c40f", "non_respondents" = "#95a5a6"),
                    labels = c("donators" = "Donators", "non_compliers" = "Non-compliers",   "non_donators" = "Non-donators", "screened_out" = "Screened out", "non_respondents" = "Non-respondents")) +
  theme_minimal()
hist_plot_all
```

```{r}
dfper <- data.frame(df_res_nosc$oplzon, as.factor(df_res_nosc$status))
#table(dfper)
#prop.table(table(dfper),1)
probs <- data.frame(prop.table(table(dfper),1))
probs$Freq <- probs$Freq*100
colnames(probs) <- c("oplzon", "status", "Freq")
#colnames(probs)
#probs
```

```{r}
hist_plot_all <- ggplot(probs, aes(x = oplzon, y = Freq, fill = status)) +
  geom_bar(stat = "identity", position = "stack", alpha = 0.7) +
  labs(
    title = "Donation Status",
    x = "Education (1 - primary, 6 - WED)",
    y = "Percentage"
  )  +
  scale_fill_manual(values = c("donators" = "#FF5733", "non_compliers" = "#3498db", "non_donators" = "#27ae60", "screened_out" = "#f1c40f", "non_respondents" = "#95a5a6"),
                    labels = c("donators" = "Donators", "non_compliers" = "Non-compliers", "non_donators" = "Non-donators", "screened_out" = "Screened out", "non_respondents" = "Non-respondents"))  +
  scale_y_continuous(labels = scales::percent_format(scale = 1), expand = c(0, 0)) +
  theme_minimal()
hist_plot_all
```


```{r}
rm(dfper, probs, hist_plot_all, hist_plot_all, lissback, filtered_df)
```

## Save the full dataset

```{r}
write.csv(df_res, "C:/Users/danch/OneDrive/2 Course MS/Thesis/Data/df_full.csv")
write.csv(df_res_trim, "C:/Users/danch/OneDrive/2 Course MS/Thesis/Data/df_full_trim.csv")
write.csv(df_res_nosc, "C:/Users/danch/OneDrive/2 Course MS/Thesis/Data/df_fullsc.csv")
```

clean environment

```{r}
rm(df_res, df_res_trim, df_res_nosc, df_liss, df_whatapp, hist_plot_all_2)
```

