---
title: "Code_exp"
output: html_document
date: "2023-11-13"
---

## Load packages and data

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(haven)
library(psych)
library(mice)
```

```{r}
df <- read_sav(".../DTD-donation/Study 1/Data/L_Datadonation_main_1.0p.sav")
keys <- read_sav(".../DTD-donation/Study 1/Data/L_Datadonation_with_non_donators.sav")
```

## Data Wrangling

### Preliminary exploration

The questionnaire was administered as a split-run study: the questionnaire was given to 800 panel members in February and presented to 4,000 panel members in April. The split-run design was chosen for a good estimate to be able to determine which percentage of the response would be successful DDPs would donate and in which ratio (chat and account packages). Based on the response percentages in split 1 (February). a good estimate can be made of the required sample size for split 2 (April).

```{r}
sort(unique(df$AccountPackageID)) # Some file are presented in the split file. Some are not.
sort(unique(df$ChatPackageID)) # Again, Some file are presented in the split file. Some are not.
length(unique(df$AccountPackageID)) # 350
length(unique(df$ChatPackageID)) # 461
length(unique(df$ChatPackageID)) + length(unique(df$AccountPackageID)) # 809
```

The questionnaire was submitted to a total of 4,800 panel members. 3,220 respondents completed the questionnaire completely (response rate 67.1%). Ultimately, 460 group chat packages were donated and 349 account information packets.

```{r}
# We can calculate donation rate, excluding those who cannot donate for diff reasons. Should be corrected for it.
table(df$account_exclude1)
table(df$account_exclude2)
table(df$account_exclude3)
table(df$account_exclude4)
table(df$account_exclude5)
table(df$account_exclude6)
table(df$account_exclude7)
```

there was package donated which stated "declined", there might be the case that there is a donation but the donation is actually absent, so it was before and it should be check.

### Data Selection & Cleaning

-   Drop non-relevant character variables with *Answer type: Text*, decrease dataframe width. 

```{r}
# Identify character columns
char_columns <- sapply(df, is.character)

# Drop character columns
lisswhat <- df[, !char_columns]
```

-   Check for and handle outliers, if any.

```{r}
# Check for outliers - if answer was not given as a range
summary(lisswhat)

# some variables look suspicious - we will leave a remark for now:
max(na.omit(lisswhat$QA11)) # Since you started using WhatsApp, how many different people have you had personal (i.e. 1 on 1) contact via WhatsApp?
max(na.omit(lisswhat$QA13)) # How many WhatsApp groups are you currently a member of?
```

Other variables, both categorical and numeric (such as income) look fine.

### Data Format Inspection

-   Inspect the data to understand its structure, variable names, and data types.

```{r}
str(lisswhat) # attributes are given, which is good
# also, most categorical variables are encoded as numeric
```

### Missing Data Handling

-   Identify and visualize missing data patterns.

```{r}
md.pattern(lisswhat)
```

Looks like we have a lot of missing data. However, practically we will need only few of the variables to be imputed - those used in some of the models.

-   Calculate the percentage of missing values for each variable.

```{r}
colSums(is.na(lisswhat)) / nrow(lisswhat) * 100

# top 30 variables by number of missing values
sort(colSums(is.na(lisswhat)), decreasing = TRUE)[1:30]

# next 30 variables
sort(colSums(is.na(lisswhat)), decreasing = TRUE)[31:60]
```

It is not yet clear how some missing values appear - for example, for _exclude class variables. We will have to check it later. For some variables, it is clear that missingness indicates that the data was donated. 

### Create Indicators for non-donation

```{r}
### non-eligible (screened-out) ###

# There is actually 1 more group - Those who do not have whatsapp etc. they were not even asked a question whether they want to donate. How their relationship to non-respondents might look like.

df$account_exclude_sum <- rowSums(df[,c("account_exclude1", "account_exclude2", "account_exclude3", "account_exclude4", "account_exclude5", "account_exclude6")], na.rm = TRUE)

df$chat_exclude_sum <- rowSums(df[,c("chat_exclude1", "chat_exclude2", "chat_exclude3", "chat_exclude4", "chat_exclude5", "chat_exclude6")], na.rm = TRUE)

# check NA
sum(is.na(df$account_exclude_sum))
sum(is.na(df$chat_exclude_sum))

# Convert to binary vectors
df$account_exclude_sum[df$account_exclude_sum > 0] <- 1
df$chat_exclude_sum[df$chat_exclude_sum > 0] <- 1

# tables
table(df$account_exclude_sum)
table(df$chat_exclude_sum)
table(df$account_exclude_sum, df$chat_exclude_sum) # some can donate only account data, but not vise versa

# create a variable for sreened out

df$screened_out <- df$account_exclude_sum + df$chat_exclude_sum
df$screened_out[df$screened_out > 1] <- 1
table(df$screened_out)

### non-respondents ###

# 4,800 - Selection of number of household members
# 1,202 - reported nonresponse, not included in the dataframe.
# 3,598 - respondents

# Make a variable for all the people who were invited and who responded to the survey participation

### non-compliers ###

# Reformat to binary
non_compliers_1 <- df$account_exclude7
non_compliers_1[is.na(non_compliers_1)] <- 0  # 1 - Yes, does not want to donate

non_compliers_2 <- df$chat_exclude7 
non_compliers_2[is.na(non_compliers_2)] <- 0 # 1 - Yes, does not want to donate

# check NA
sum(is.na(non_compliers_1))
sum(is.na(non_compliers_2))

# Tables
table(non_compliers_1)
table(non_compliers_2)
table(non_compliers_1, non_compliers_2) # perfect intersection

# Create a variable for non-compliers
df$non_compliers <- non_compliers_1 + non_compliers_2
df$non_compliers[df$non_compliers > 0] <- 1

## THOSE are all who disagreed to donate

## now, we encode only those non-compliers who had the means to donate at least account data, but still disagreed

df$non_compliers_actual <- df$non_compliers - df$account_exclude_sum
df$non_compliers_actual[df$non_compliers_actual < 0] <- 0

### donators ### 
# presence of donated package hash, donated at least 1 thing

# check NA

df$AccountPackageID
df$ChatPackageID

# Convert to binary vector of donators

donators_1 <- ifelse(df$AccountPackageID == "", 0, 1)
donators_2 <- ifelse(df$ChatPackageID == "", 0, 1)

df$donators <- donators_1 + donators_2
df$donators[df$donators > 0] <- 1

### non-donators ### 
# absence of donated package hash (ChatPackageID, AccountPackageID) minus non-compliers
df$non_donators <- 1 - df$donators - df$non_compliers 
table(df$non_donators)

# explore respondents with -1 value
indices <- which(df$non_donators == -1)
indices

# recode as donators
df$non_donators[indices] <- 0
df$non_donators[df$non_donators < 0] <- 0

# also, lets create a categorical variable showing status

table(df$donators, df$screened_out)
table(df$donators, df$non_compliers_actual)
table(df$donators, df$non_donators)

# refusal conversion as donated
df$non_compliers_actual[df$donators == 1] <- 0
df$screened_out[df$donators == 1] <- 0

df$status <-  ifelse(df$screened_out == 1, "screened_out", ifelse(df$non_compliers_actual == 1, "non_compliers", ifelse(df$non_donators == 1, "non_donators", "donators")))
table(df$status)
```

### Descriptive Analysis

-   Calculate summary statistics like mean, median, and standard deviation.

```{r}
describe(lisswhat)
```

Tables

```{r}
apply(lisswhat[,6:19], 2, table) #exclusion factors
```

These variables are the same, they just duplicate each other.

Now, lets address subsets

```{r}
df_screened_out <- subset(df, screened_out == 1)
df_non_compliers <- subset(df, non_compliers_actual == 1 & df$screened_out == 0, )
df_non_donators <- subset(df, non_donators == 1)
df_donators <- subset(df, donators == 1)
```

### Univariate Analysis

-   Visualize the distribution of control variables using histograms, density plots, or bar charts.

```{r}
hist_plot <- ggplot(df, aes(x = leeftijd, fill = factor(donators))) +
  geom_histogram(binwidth = 0.5, position = "identity", alpha = 0.7) +
  labs(
    title = "Donation Status",
    x = "Age",
    y = "Frequency"
  ) +
  scale_fill_manual(values = c("0" = "red", "1" = "blue"),
                    labels = c("0" = "Non-Donators", "1" = "Donators")) +
  theme_minimal()
hist_plot

hist_plot_all <- ggplot(df, aes(x = leeftijd, fill = factor(status))) +
  geom_histogram(binwidth = 0.5, alpha = 0.7) +
  labs(
    title = "Donation Status",
    x = "Age",
    y = "Frequency"
  )  +
  scale_fill_manual(values = c("donators" = "#FF5733", "non_compliers" = "#3498db",   "non_donators" = "#27ae60", "screened_out" = "#f1c40f"),
                    labels = c("donators" = "Donators", "non_compliers" = "Non-compliers",   "non_donators" = "Non-donators", "screened_out" = "Screened out")) +
  theme_minimal()
hist_plot_all
```

They can be reordered here, in the graph 

```{r}
hist_plot_all <- ggplot(df, aes(x = sted, fill = factor(status))) +
  geom_histogram(binwidth = 0.5, alpha = 0.7) +
  labs(
    title = "Donation Status",
    x = "Urbanisation (1 - strongly urban)",
    y = "Frequency"
  )  +
  scale_fill_manual(values = c("donators" = "#FF5733", "non_compliers" = "#3498db",   "non_donators" = "#27ae60", "screened_out" = "#f1c40f"),
                    labels = c("donators" = "Donators", "non_compliers" = "Non-compliers",   "non_donators" = "Non-donators", "screened_out" = "Screened out")) +
  theme_minimal()
hist_plot_all
```

```{r}
filtered_df <- df[df$brutoink < 15000, ]

hist_plot_all <- ggplot(filtered_df, aes(x = brutoink, fill = factor(status))) +
  geom_density(alpha = 0.5) +
  labs(
    title = "Donation Status",
    x = "Income",
    y = "Frequency"
  )  +
  scale_fill_manual(values = c("donators" = "#FF5733", "non_compliers" = "#3498db", "non_donators" = "#27ae60", "screened_out" = "#f1c40f"),
                    labels = c("donators" = "Donators", "non_compliers" = "Non-compliers",   "non_donators" = "Non-donators", "screened_out" = "Screened out")) +
  theme_minimal()
hist_plot_all
```


```{r}
hist_plot_all <- ggplot(df, aes(x = oplzon, fill = factor(status))) +
  geom_histogram(binwidth = 0.5, alpha = 0.7) +
  labs(
    title = "Donation Status",
    x = "Education (1 - primary, 6 - WED)",
    y = "Frequency"
  )  +
  scale_fill_manual(values = c("donators" = "#FF5733", "non_compliers" = "#3498db",   "non_donators" = "#27ae60", "screened_out" = "#f1c40f"),
                    labels = c("donators" = "Donators", "non_compliers" = "Non-compliers",   "non_donators" = "Non-donators", "screened_out" = "Screened out")) +
  theme_minimal()
hist_plot_all
```


```{r}
hist_plot_all <- ggplot(df, aes(x = geslacht, fill = factor(status))) +
  geom_histogram(binwidth = 0.5, alpha = 0.7) +
  labs(
    title = "Donation Status",
    x = "Sex (1 - male, 2 - female 3 - other)",
    y = "Frequency"
  )  +
  scale_fill_manual(values = c("donators" = "#FF5733", "non_compliers" = "#3498db",   "non_donators" = "#27ae60", "screened_out" = "#f1c40f"),
                    labels = c("donators" = "Donators", "non_compliers" = "Non-compliers",   "non_donators" = "Non-donators", "screened_out" = "Screened out")) +
  theme_minimal()
hist_plot_all
```

## Export Data

### Attach nomem_encr for non-respondents to the full dataframe

```{r}
df$non_respondents <- 0
nomem_encr <- full_join(df, keys, by = c("nomem_encr"))

nomem_encr <- nomem_encr %>% 
  mutate(donators = replace_na(donators, 0),
         non_compliers = replace_na( non_compliers, 0),
         non_donators = replace_na( non_donators, 0),
         non_respondents = replace_na( non_respondents, 1),
         non_compliers_actual = replace_na(non_compliers_actual, 0),
         screened_out = replace_na(screened_out, 0),
         status = replace_na(status, "non_respondents"))
```

### Save exported file

```{r}
write.csv(nomem_encr, ".../DTD-donation/Study 1/Data/df_what.csv")
```
