---
title: "Explore_script_fulldata"
output: html_document
date: "2024-02-16"
---

## Load packages and data

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(haven)
library(psych)
```

## Data wrangling

### Data selection & cleaning

load all variables

```{r}
df <- read.csv(".../DTD-donation/Study 1/Data/df_what.csv", header=TRUE)[,2:166]
df_liss <- read.csv(".../DTD-donation/Study 1/Data/df_liss.csv", header=TRUE)[,2:131]
lissback <- read_sav(".../DTD-donation/Study 1/Data/avars_202309_EN_1.0p.sav")
```

detach control variables

```{r}
df <- df[,-c(125:156)]
df_liss <- df_liss[,-c(2:34)]
```

join dataframes, attach liss panels to a whats app study

```{r}
df_res <- df %>% 
  left_join(df_liss, by = "nomem_encr")
```

attach control variables

```{r}
df_res <- df_res %>% 
  left_join(lissback, by = "nomem_encr")
```

## Exploratory Analysis

### Descriptive Analysis

-   Calculate summary statistics like mean, median, and standard deviation.

```{r}
describe(df_res)
```

### Univariate Analysis for controls

We provide exploratory visualizations to check distributions and splits by type of non-donation. 

```{r}
hist_plot_all <- ggplot(df_res, aes(x = leeftijd, fill = factor(status))) +
  geom_histogram(binwidth = 0.5, alpha = 0.7) +
  labs(
    title = "Donation Status",
    x = "Age",
    y = "Frequency"
  )  +
  scale_fill_manual(values = c("donators" = "#FF5733", "non_compliers" = "#3498db",   "non_donators" = "#27ae60", "screened_out" = "#f1c40f", "non_respondents" = "#95a5a6"),
                    labels = c("donators" = "Donators", "non_compliers" = "Non-compliers",   "non_donators" = "Non-donators", "screened_out" = "Screened out", "non_respondents" = "Non-respondents")) +
  scale_x_continuous(breaks = seq(0, 100, by = 5)) +
  scale_y_continuous(breaks = seq(0, 100, by = 5)) +
  theme_minimal()
hist_plot_all
```

```{r}
dfper <- data.frame(df_res$leeftijd, as.factor(df_res$status))
table(dfper)
prop.table(table(dfper),1)
probs <- data.frame(prop.table(table(dfper),1))
probs$Freq <- probs$Freq*100
colnames(probs) <- c("leeftijd", "status", "Freq")
colnames(probs)
probs
```

Now, we plot the distribution of the variable "leeftijd" by donation status.

```{r}
hist_plot_all <- ggplot(probs, aes(x = leeftijd, y = Freq, fill = status)) +
  geom_bar(stat = "identity", position = "stack", alpha = 0.7) +
  labs(
    title = "Donation Status",
    x = "Age",
    y = "Percentage"
  )  +
  scale_fill_manual(values = c("donators" = "#FF5733", "non_compliers" = "#3498db", "non_donators" = "#27ae60", "screened_out" = "#f1c40f", "non_respondents" = "#95a5a6"),
                    labels = c("donators" = "Donators", "non_compliers" = "Non-compliers", "non_donators" = "Non-donators", "screened_out" = "Screened out", "non_respondents" = "Non-respondents"))  +
  scale_y_continuous(labels = scales::percent_format(scale = 1), expand = c(0, 0)) +
  theme_minimal()
hist_plot_all
```

Now, we drop the missing values and plot the distribution of the variable "sted" by donation status.

```{r}
filtered_df <- df_res[df_res$sted > -1, ]

hist_plot_all <- ggplot(filtered_df, aes(x = sted, fill = factor(status))) +
  geom_histogram(binwidth = 0.5, alpha = 0.7) +
  labs(
    title = "Donation Status",
    x = "Urbanisation (1 - strongly urban)",
    y = "Frequency"
  )  +
  scale_fill_manual(values = c("donators" = "#FF5733", "non_compliers" = "#3498db",   "non_donators" = "#27ae60", "screened_out" = "#f1c40f", "non_respondents" = "#95a5a6"),
                    labels = c("donators" = "Donators", "non_compliers" = "Non-compliers",   "non_donators" = "Non-donators", "screened_out" = "Screened out", "non_respondents" = "Non-respondents")) +
  theme_minimal()
hist_plot_all
```

Now, we drop the income outliers and plot the distribution of the variable "brutoink" by donation status.

```{r}
filtered_df <- df_res[df_res$brutoink < 15000, ]

hist_plot_all <- ggplot(filtered_df, aes(x = brutoink, fill = factor(status))) +
  geom_density(alpha = 0.5) +
  labs(
    title = "Donation Status",
    x = "Income",
    y = "Frequency"
  )  +
  scale_fill_manual(values = c("donators" = "#FF5733", "non_compliers" = "#3498db",   "non_donators" = "#27ae60", "screened_out" = "#f1c40f", "non_respondents" = "#95a5a6"),
                    labels = c("donators" = "Donators", "non_compliers" = "Non-compliers",   "non_donators" = "Non-donators", "screened_out" = "Screened out", "non_respondents" = "Non-respondents")) +
  theme_minimal()
hist_plot_all
```

Now, we drop the missing values and plot the distribution of the variable "opleid", education, by donation status.

```{r}
hist_plot_all <- ggplot(df_res, aes(x = oplzon, fill = factor(status))) +
  geom_histogram(binwidth = 0.5, alpha = 0.7) +
  labs(
    title = "Donation Status",
    x = "Education (1 - primary, 6 - WED)",
    y = "Frequency"
  )  +
  scale_fill_manual(values = c("donators" = "#FF5733", "non_compliers" = "#3498db",   "non_donators" = "#27ae60", "screened_out" = "#f1c40f", "non_respondents" = "#95a5a6"),
                    labels = c("donators" = "Donators", "non_compliers" = "Non-compliers",   "non_donators" = "Non-donators", "screened_out" = "Screened out", "non_respondents" = "Non-respondents")) +
  theme_minimal()
hist_plot_all
```

```{r}
dfper <- data.frame(df_res$oplzon, as.factor(df_res$status))
table(dfper)
prop.table(table(dfper),1)
probs <- data.frame(prop.table(table(dfper),1))
probs$Freq <- probs$Freq*100
colnames(probs) <- c("oplzon", "status", "Freq")
colnames(probs)
probs
```

```{r}
hist_plot_all <- ggplot(probs, aes(x = oplzon, y = Freq, fill = status)) +
  geom_bar(stat = "identity", position = "stack", alpha = 0.7) +
  labs(
    title = "Donation Status",
    x = "Education (1 - primary, 6 - WED)",
    y = "Percentage"
  )  +
  scale_fill_manual(values = c("donators" = "#FF5733", "non_compliers" = "#3498db", "non_donators" = "#27ae60", "screened_out" = "#f1c40f", "non_respondents" = "#95a5a6"),
                    labels = c("donators" = "Donators", "non_compliers" = "Non-compliers", "non_donators" = "Non-donators", "screened_out" = "Screened out", "non_respondents" = "Non-respondents"))  +
  scale_y_continuous(labels = scales::percent_format(scale = 1), expand = c(0, 0)) +
  theme_minimal()
hist_plot_all
```

```{r}
hist_plot_all <- ggplot(df_res, aes(x = geslacht, fill = factor(status))) +
  geom_histogram(binwidth = 0.5, alpha = 0.7) +
  labs(
    title = "Donation Status",
    x = "Sex (1 - male, 2 - female 3 - other)",
    y = "Frequency"
  )  +
  scale_fill_manual(values = c("donators" = "#FF5733", "non_compliers" = "#3498db",   "non_donators" = "#27ae60", "screened_out" = "#f1c40f", "non_respondents" = "#95a5a6"),
                    labels = c("donators" = "Donators", "non_compliers" = "Non-compliers",   "non_donators" = "Non-donators", "screened_out" = "Screened out", "non_respondents" = "Non-respondents")) +
  theme_minimal()
hist_plot_all
```

### Univariate analysis for the independent variables

Here we do the same, but IVs of interest are used instead of controls

```{r}
hist_plot_all <- ggplot(df_res, aes(x = cp23o019, fill = factor(status))) +
  geom_histogram(binwidth = 0.5, alpha = 0.7) +
  labs(
    title = "Generalized Trust Question",
    x = "(1 - can't be too careful; 10 - Most people can be trusted)",
    y = "Frequency"
  )  +
  scale_fill_manual(values = c("donators" = "#FF5733", "non_compliers" = "#3498db",   "non_donators" = "#27ae60", "screened_out" = "#f1c40f", "non_respondents" = "#95a5a6"),
                    labels = c("donators" = "Donators", "non_compliers" = "Non-compliers",   "non_donators" = "Non-donators", "screened_out" = "Screened out", "non_respondents" = "Non-respondents")) +
  theme_minimal()
hist_plot_all
```

Filter out the missing values and plot the distribution of the variable "org_env" by donation status.

```{r}
filtered_df <- df_res
filtered_df$org_env_binary <- ifelse(filtered_df$org_env == "no connection", 0, 1)
filtered_df$org_hum_binary <- ifelse(filtered_df$org_hum == "no connection", 0, 1)

hist_plot_all <- ggplot(filtered_df, aes(x = org_hum_binary, fill = factor(status))) +
  geom_histogram(binwidth = 0.5, alpha = 0.7) +
  labs( title = "Altruism Question")  +
  scale_fill_manual(values = c("donators" = "#FF5733", "non_compliers" = "#3498db",   "non_donators" = "#27ae60", "screened_out" = "#f1c40f", "non_respondents" = "#95a5a6"),
                    labels = c("donators" = "Donators", "non_compliers" = "Non-compliers",   "non_donators" = "Non-donators", "screened_out" = "Screened out", "non_respondents" = "Non-respondents")) +
  theme_minimal()

hist_plot_all_2 <- ggplot(filtered_df, aes(x = org_env_binary, fill = factor(status))) +
  geom_histogram(binwidth = 0.5, alpha = 0.7) +
  labs( title = "Altruism Question")  +
  scale_fill_manual(values = c("donators" = "#FF5733", "non_compliers" = "#3498db",   "non_donators" = "#27ae60", "screened_out" = "#f1c40f", "non_respondents" = "#95a5a6"),
                    labels = c("donators" = "Donators", "non_compliers" = "Non-compliers",   "non_donators" = "Non-donators", "screened_out" = "Screened out", "non_respondents" = "Non-respondents")) +
  theme_minimal()

hist_plot_all
hist_plot_all_2
```

## Exploratory Analysis (Screened-out respondents excluded)

```{r}
df_res_nosc <- df_res[df_res$status != "screened_out",]
```

### Descriptive Analysis

```{r}
describe(df_res)
```

### Univariate Analysis for all

Again, we provide different plots for the variables of interests showed by group, type of donation/non-donation for exploratory purposes.

```{r}
hist_plot_all <- ggplot(df_res_nosc, aes(x = leeftijd, fill = factor(status))) +
  geom_histogram(binwidth = 0.5, alpha = 0.7) +
  labs(
    title = "Donation Status",
    x = "Age",
    y = "Frequency"
  )  +
  scale_fill_manual(values = c("donators" = "#FF5733", "non_compliers" = "#3498db",   "non_donators" = "#27ae60", "screened_out" = "#f1c40f", "non_respondents" = "#95a5a6"),
                    labels = c("donators" = "Donators", "non_compliers" = "Non-compliers",   "non_donators" = "Non-donators", "screened_out" = "Screened out", "non_respondents" = "Non-respondents")) +
  scale_x_continuous(breaks = seq(0, 100, by = 5)) +
  scale_y_continuous(breaks = seq(0, 100, by = 5)) +
  theme_minimal()
hist_plot_all
```

```{r}
dfper <- data.frame(df_res_nosc$leeftijd, as.factor(df_res_nosc$status))
#table(dfper)
#prop.table(table(dfper),1)
probs <- data.frame(prop.table(table(dfper),1))
probs$Freq <- probs$Freq*100
colnames(probs) <- c("leeftijd", "status", "Freq")
#colnames(probs)
#probs
```



```{r}
hist_plot_all <- ggplot(probs, aes(x = leeftijd, y = Freq, fill = status)) +
  geom_bar(stat = "identity", position = "stack", alpha = 0.7) +
  labs(
    title = "Donation Status",
    x = "Age",
    y = "Percentage"
  )  +
  scale_fill_manual(values = c("donators" = "#FF5733", "non_compliers" = "#3498db", "non_donators" = "#27ae60", "screened_out" = "#f1c40f", "non_respondents" = "#95a5a6"),
                    labels = c("donators" = "Donators", "non_compliers" = "Non-compliers", "non_donators" = "Non-donators", "screened_out" = "Screened out", "non_respondents" = "Non-respondents"))  +
  scale_y_continuous(labels = scales::percent_format(scale = 1), expand = c(0, 0)) +
  theme_minimal()
hist_plot_all
```


```{r}
hist_plot_all <- ggplot(df_res_nosc, aes(x = oplzon, fill = factor(status))) +
  geom_histogram(binwidth = 0.5, alpha = 0.7) +
  labs(
    title = "Donation Status",
    x = "Education (1 - primary, 6 - WED)",
    y = "Frequency"
  )  +
  scale_fill_manual(values = c("donators" = "#FF5733", "non_compliers" = "#3498db",   "non_donators" = "#27ae60", "screened_out" = "#f1c40f", "non_respondents" = "#95a5a6"),
                    labels = c("donators" = "Donators", "non_compliers" = "Non-compliers",   "non_donators" = "Non-donators", "screened_out" = "Screened out", "non_respondents" = "Non-respondents")) +
  theme_minimal()
hist_plot_all
```

```{r}
dfper <- data.frame(df_res_nosc$oplzon, as.factor(df_res_nosc$status))
#table(dfper)
#prop.table(table(dfper),1)
probs <- data.frame(prop.table(table(dfper),1))
probs$Freq <- probs$Freq*100
colnames(probs) <- c("oplzon", "status", "Freq")
#colnames(probs)
#probs
```

```{r}
hist_plot_all <- ggplot(probs, aes(x = oplzon, y = Freq, fill = status)) +
  geom_bar(stat = "identity", position = "stack", alpha = 0.7) +
  labs(
    title = "Donation Status",
    x = "Education (1 - primary, 6 - WED)",
    y = "Percentage"
  )  +
  scale_fill_manual(values = c("donators" = "#FF5733", "non_compliers" = "#3498db", "non_donators" = "#27ae60", "screened_out" = "#f1c40f", "non_respondents" = "#95a5a6"),
                    labels = c("donators" = "Donators", "non_compliers" = "Non-compliers", "non_donators" = "Non-donators", "screened_out" = "Screened out", "non_respondents" = "Non-respondents"))  +
  scale_y_continuous(labels = scales::percent_format(scale = 1), expand = c(0, 0)) +
  theme_minimal()
hist_plot_all
```

Now, we save joined dataframes:

```{r}
write.csv(df_res, "C.../DTD-donation/Study 1/Data/df_full.csv")
write.csv(df_res_nosc, ".../DTD-donation/Study 1/Data/df_fullsc.csv")
```
